---
title: "Assignment0_ThierryMartin"
author: "Thierry Martin"
date: "January 31, 2017"
output: html_document
---

##### ToDo 1:

Result:
`r ((2017-2015)/(2017-1997))*100`

Comment: r must be used before every r code to make it function correctly in R Markdown.
#### ToDo 2:

Result:
`r ToDo2= ((2017-2015)/(2017-1997))*100
ToDo2`

#### ToDo 3:

Result:
`r sum(4,5,8,11)`

#### ToDo 4:

Result:
```{r, out.width = '\\maxwidth'}
plot(rnorm(100))
```

Comment: To make the plot display using R Markdown you need to add {r} before the plot code, you can even add the desired with and things of that order to make the plot display the way you desire. 

#### ToDo 5:

Result:
`r help(sqrt)`

#### ToDo 6:

Result:
r lapply(1:10, function(n)source("firstscript.R")$value)

```{r, out.width = '\\maxwidth'}
plot(rnorm(100))
```

Comment: This scrip must exits and R needs to have access to the script for it to run, therefore I made the appropriate r code, but the code is only displayed, it is not the actual running code. 

#### ToDo 7:

Result:
`r P = seq(from=31, to=60, by=1)
Q= matrix(P,ncol = 5, nrow = 6)
P`

Comment: I am having trouble displaying the Q matrix in R Markdown, however the code to create Q is in the R Markdown document, Q= matrix(P,ncol = 5, nrow = 6). I can make this work in the Console however by simply entering Q. 

#### ToDo 8:

Result:
```{r, out.width = '\\maxwidth'}
x1=seq(from=1, to=100, by=1)
x2=seq(from=101, to=200, by=1)
x3=seq(from=201, to=300, by=1)
t= data.frame(a=x1,b=x1+x2,c=x1+x2+x3)
plot(t)
```

#### ToDo 9:

Result:
```{r, out.width = '\\maxwidth'}
plot(t$a, type="l", ylim=range(t),lwd=3, col=rgb(1,0,0,0.3))
lines(t$b, type="s", lwd=2,col=rgb(0.3,0.4,0.3,0.9))
points(t$c, pch=20, cex=4,col=rgb(0,0,1,0.3))
```

#### ToDo 10:

Result:
`r sqrt(mean(rnorm(100)))`

Comment: It is possible to receive NaNs or an error because of the NaNs result, it is produced when the resulting value is negative, run Knit again in R Markdown t'ill you receive a result.

#### ToDo 11:

Result:
`r d = data.frame(g = c(3,4,5),h = c(12,43,54))
write.table(d, file="tst1.txt", row.names=FALSE)
d2 = read.table(file="tst1.txt",header=TRUE)
d2$g*5`

#### ToDo 12:

r 
date1=strptime( c("20170131","20170303"),format="%Y%m%d")
present=c(0,1)
date1

Comment: This code is simply displayed, it works in the Console, but I cant seem to make it work in R Markdown.

#### ToDo 13

Result:

`r 

vector=seq(from=1, to=100, by=1)
s=c()
for(i in 1:100)
{
  if(vector[i]<5)
  {
    s[i]=vector[i]*5;
  }
  else if(vector[i]>90)
  {
    s[i]=vector[i]*10;
  }
  else
  {
    s[i]=vector[i]*0.1;
  }
}
s`

#### ToDo 14:

`r

fun= function(arg1,arg2 )
{
  vector[i]=arg1[i];
  for(i in length(vector))
  {
    
  }
}
`
